Toward Supervised Reinforcement Learning with Partial States for Social HRI

### 2017-07-26 paper.tex
Reorganisation
Update on Overleaf.

\def\year{2017}\relax
%File: formatting-instruction.tex
\documentclass[letterpaper]{article} %DO NOT CHANGE THIS
\usepackage{aaai17}  %Required
\usepackage{times}  %Required
\usepackage{helvet}  %Required
\usepackage{courier}  %Required
\usepackage{url}  %Required
\usepackage{graphicx}  %Required
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{comment}
\usepackage{amssymb}
\usepackage{subcaption}
\frenchspacing  %Required
\setlength{\pdfpagewidth}{8.5in}  %Required
\setlength{\pdfpageheight}{11in}  %Required
%PDF Info Is Required:
  \pdfinfo{
/Title (Supervised Reinforcement Learning with Partial States: a Teaching Method for Action Selection for HRI)
/Author (Emmanuel Senft)}
\setcounter{secnumdepth}{0}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Supervised Reinforcement Learning with Partial States: \\
 a Teaching Method for Action Selection for HRI}

>>>>

\def\year{2017}\relax
%File: formatting-instruction.tex
\documentclass[letterpaper]{article} %DO NOT CHANGE THIS
\usepackage{aaai17}  %Required
\usepackage{times}  %Required
\usepackage{helvet}  %Required
\usepackage{courier}  %Required
\usepackage{url}  %Required
\usepackage{graphicx}  %Required
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{comment}
\usepackage{amssymb}
\usepackage{subcaption}
\frenchspacing  %Required
\setlength{\pdfpagewidth}{8.5in}  %Required
\setlength{\pdfpageheight}{11in}  %Required
%PDF Info Is Required:
  \pdfinfo{
/Title (Toward Supervised Reinforcement Learning with Partial States for Social HRI)
/Author (Emmanuel Senft)}
\setcounter{secnumdepth}{0}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Toward Supervised Reinforcement Learning with Partial States for Social HRI}
